% Created 2023-02-27 Mon 18:26
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Sergi Simón Balcells}
\date{\today}
\title{Thesis}
\hypersetup{
 pdfauthor={Sergi Simón Balcells},
 pdftitle={Thesis},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.6)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents



\section{{\bfseries\sffamily PROJ} RoadMap to write thesis}
\label{sec:org587f28d}
\begin{itemize}
\item[{$\boxtimes$}] What to include?
\item[{$\boxtimes$}] Sections
\end{itemize}
\subsection{Previous work}
\label{sec:org017a5ec}
\url{https://recsi2022.unican.es/wp-content/uploads/2022/10/LibroActas-978-84-19024-14-5.pdf}

\section{{\bfseries\sffamily TODO} Abstract}
\label{sec:orgdaf8c78}
\begin{itemize}
\item[{$\square$}] Dunno, base it on previous work
\end{itemize}
An on-line forum is a platform which enables users to post messages which become available to any
person with access to it. In this articles, we focus on forums which preserve the anonymity of a
user while being authenticated. More concretely, in this paper we improve an existing scheme.

Index terms - cryptography, discussion board, privacy, ring signature
\section{{\bfseries\sffamily TODO} Introduction}
\label{sec:orgf1b61fe}
\begin{itemize}
\item[{$\boxtimes$}] Forum signature use case
\item[{$\boxtimes$}] Signatures schemas: ring and group
\item[{$\boxtimes$}] \sout{Previous work} would be in caveats of previous approach
\end{itemize}

Enterprises, city halls and educators found a way to guarantee anonymous feedback by providing a mail box
where people could post a message without specifying who it was. This enabled workers, citizens and students
to provide feedback without any chances of having repercussions for critisizing them. At the same time, as the location of them was inside of the enterprise, city and eductional center, the readers could assert with some
security that the writer was, in fact, an employee, a citizen, and a student.

With the arrival of the Internet, some of these activities could be totaly online, as a remote
office, so it made appearent that there is a need for a security protocol that preserves the
anonymity of the poster while it makes sure that the writer is an authenticated user. This use case
will be refered as a forum in this paper.

Such cryptographic system should provide a means to authenticate, so only users can post messages. The users
should remain anonymous, as the identity of the message author is not revealed. Additionally, messages from the same user should remain unlinkable.

For this cryptographic schemes, a Group signature \cite{group} could provide the required security purposes. However, this cryptographic scheme includes a trusted group manager, who is able to revoke the anonymity of the writer when required. To overcome this difficulty, the protocol described here will user a similar tool, namely ring signatures \cite{ring}. This does not require its users to trust the entity with the exception of
certificate authorities issuing public key certificates.

\section{Preliminaries}
\label{sec:org9952df9}
\begin{itemize}
\item[{$\square$}] Group signature
\item[{$\square$}] Ring Signature
\item[{$\square$}] Internet writer distribution
\end{itemize}

\section{{\bfseries\sffamily TODO} Caveats of previous approach}
\label{sec:org17fe0d9}
\begin{itemize}
\item[{$\square$}] bad start makes different for weight
\item[{$\square$}] bad if user changes habits
\item[{$\square$}] depending on weight, bad for lurker or bad for super users
\end{itemize}
\section{{\bfseries\sffamily TODO} Window approach}
\label{sec:orgc4c8175}
\begin{itemize}
\item[{$\square$}] window of last n messages
\item[{$\square$}] simplified complexity if the forum grows larger
\item[{$\square$}] computes weight based on that, so there is a maximum weight possible
\end{itemize}
\section{{\bfseries\sffamily TODO} Results}
\label{sec:org83f7a87}
\begin{itemize}
\item[{$\square$}] add graphic distribution of anonymity
\begin{itemize}
\item[{$\square$}] explain that if users have the same amount of signatures but one has
low anonymity while other high, then you have less chance to get the correct user
\end{itemize}
\item[{$\square$}] add caveat of first message
\begin{itemize}
\item[{$\square$}] explain that in simulations, it has even better anonymity than normal
\end{itemize}
\item[{$\square$}] Add boxplots of anonymity of users.
\end{itemize}

\section{{\bfseries\sffamily TODO} Conclusions}
\label{sec:org6b64139}
\begin{itemize}
\item[{$\square$}] Window is a superior approach to forum schemes.
\end{itemize}
\section{{\bfseries\sffamily TODO} Acknowledgements}
\label{sec:orgeb5bfc5}
\begin{itemize}
\item[{$\square$}] I don't know if I have any
\end{itemize}
\section{{\bfseries\sffamily TODO} References}
\label{sec:org11e70d0}
\begin{itemize}
\item[{$\square$}] The eight references of my life.
\item[{$\square$}] delete this, as the latex block takes care already
\end{itemize}


\bibliography{bib}
\bibliographystyle{ieeetr}
\end{document}